\papertitle

### 2014-03-20 final-report/paper.tex
network viz section

The Worker Communication view consists of two charts: the aggregate communication 
chart and the time series chart. The aggregate communication chart is a matrix representing
a cluster of $N$ workers. Each cell $m,n$ in the matrix represents the total number of tuples sent
by worker $m$ to worker $n$ during the query execution. Figure \ref{fig:matrix} shows this chart along 
with the selected link in the query plan DAG.

\begin{figure}[ht]
  \includegraphics[width=\columnwidth]{images/networkVis1}
  \caption{Worker communication matrix chart.}
  \label{fig:matrix}
\end{figure}

\section{Evaluation}

>>>>

The Worker Communication view consists of two charts: the aggregate communication 
chart and the time series chart. The aggregate communication chart is a matrix representing
a cluster of $N$ workers. Each cell $m,n$ in the matrix represents the total number of tuples sent
by worker $m$ to worker $n$ during the query execution. Figure \ref{fig:matrix} shows this chart along 
with the selected link in the query plan DAG. Hovering the mouse over a cell brings up a tooltip
stating the total number of tuples exchanged between the source and destination workers. The intensity
of the cell color reflects the number of tuples exchanged, i.e., a larger number translates into a darker color 
and a smaller number results in a lighter color. The color pallet used is immune to color-blindness issues.
The matrix chart representing aggregate communication 
between workers help uncover data skew issues, as discussed in \S \ref{sec:eval}.

We initially considered having a chord diagram\footnote{\url{http://bl.ocks.org/mbostock/4062006}} instead of a matrix 
for the aggregate communication chart. But feedback during the progress presentation session convinced us that 
a chord diagram would suffer from scalability problems. Adding an option for displaying a chord diagram remains
part of future work.

\begin{figure}[ht]
  \includegraphics[width=\columnwidth]{images/networkVis1}
  \caption{Worker communication matrix chart. Each cell represents the number of exchanged tuples between a 
  pair of workers.}
  \label{fig:matrix}
\end{figure}

\section{Evaluation}
\label{sec:eval}
